\begin{tcolorbox}[colback=red!5,colframe=DarkRed!40!black,title=Mars \& Curiosity: The Red Planet and the rover]
\textbf{\large{MARS}\cite{NASA-rover}}

\textbf{Location:} Mars is the 4th planet from the Sun, about 1,5 times far out as Earth.

\textbf{Size:} About half the diameter of the Earth, it is the second smallest.
A $100 kg$ person would weight $38 kg$ on Mars.

\textbf{Magnetism:} It has no spinning iron core and thus no planet-wide magnetic field.

\textbf{Orbit:} The distance from the Sun due to the elliptical orbit varies significantly more than on Earth.

\textbf{Time:} A year lasts for $687$ Earth days.
Martian day = \textit{sol} = \textit{24 hours, 39 minutes and 35 seconds}.

\textbf{Atmosphere:} The atmosphere mainly consists of carbon dioxide ($95,3 \%$), nitrogen ($2,7 \%$) and argon ($1,6\%$).
The atmosphere on Earth is almost 200 times denser than on Mars.

\textbf{Climate:} Temperatures varies between $-128C$ and $27 \degree C$ with an average of $-53 \degree C$.

\textbf{Geography:} Olympus Mons, the tallest known mountain, is $26 km$, which is approximately 3 times as tall as Mount Everest.
Valles Marineris is the solar systems' largest and deepest known system of valleys.

\textbf{Moons:} Mars has two moons: Deimos and Phobos.

\textbf{Surface:} The surface has minerals containing silicon, oxygen and metals.
Its red color comes from iron oxide.

\noindent\makebox[\linewidth]{\rule{\textwidth}{0.4pt}}
\vspace{0mm}

\textbf{\large{Curiosity}}

\textbf{Purpose:} To investigate the climate and geology on Mars, and to find evidences for the presence of water.

\textbf{Travel:} From November 26th 2011 in Miami to August 6th 2012 at the Gale Crater.

\textbf{Planned mission duration:} One Martian year, that is 98 weeks.

\textbf{Mass/size:} The mass is $900 kg$.
The dimensions are $3 m x 2,8 m x 2,1 m$, about the size of a car.

\textbf{Movement:} The rover can travel by an average of $30 m$ per hour.

\textbf{Instruments:} It has 17 cameras, most of them are used to drive and navigate.

\textbf{Energy source:} The onboard nuclear power plant carries plutonium-238.
From the material's decay it can produce $125 W$ of electricity.

\textbf{Computers:} The two identical computers are specially built to tolerate the radiation that occur on Mars.
They have only $256 MB$ of RAM and $2 GB$ of flash memory each.

\textbf{Communication:} The rover uses its three antennas to communicate in the UHF band.
Direct communication to the Earth takes about 7 minutes.
The rover can also communicate via Mars satellites.

\textbf{Cost:} The overall cost was $2,5 billion USD$, where 1,8 billion of it was used on freighting the rover to Mars.
\end{tcolorbox}