\begin{thebibliography}{99}	% Denne referanselisten kan ikke ha flere enn 99 referanser.
	\bibitem{Exoboken}
		Kjetill Østgaard
		\emph{Exobiology: A hitch-hiker's guide to alien life}
		Institutt for bioteknologi,
		NTNU,
		2000.
	\bibitem{NASA-rover}
		NASA,
		\emph{Mars Science Laboratory Launch}
		Press kit,
		November 2011.
	\bibitem{ChemCam}
		NASA,
		\emph{Chemistry \& Camera}
		http://msl-scicorner.jpl.nasa.gov/Instruments/ChemCam/,
		March 11th 2015.
	\bibitem{CheMin}
		NASA,
		\emph{Chemistry \& Mineralogy}
		http://msl-scicorner.jpl.nasa.gov/Instruments/CheMin/,
		March 24th 2015.
	\bibitem{RAD}
		NASA,
		\emph{Radiation Assessment Detector}
		http://msl-scicorner.jpl.nasa.gov/Instruments/RAD/,
		March 24th 2015.
	\bibitem{SolidWater}
		NASA,
		\emph{Ask an astrobiologist - Why is water important for life?}
		https://astrobiology.nasa.gov/ask-an-astrobiologist/answered/2002/05/01/122/,
		April 7th 2015.
	\bibitem{NASAwater}
		NASA,
		\emph{Water: Molecule of Life},
		http://www.nasa.gov/vision/universe/solarsystem/Water:\_Molecule\_of\_Life.html,
		April 8th 2015.
	\bibitem{MissionTimeline}
		NASA,
		\emph{Launch},
		http://mars.nasa.gov/msl/mission/timeline/launch/,
		April 9th 2015.
	\bibitem{NASALanding}
		NASA,
		\emph{Entry, Descent, and Landing},
		http://mars.nasa.gov/msl/mission/timeline/edl/,
		April 9th 2015.
	\bibitem{NASALanding_diag}
		NASA,
		\emph{Mars Curiosity Landing and Descent Diagram},
		http://www.startalkradio.net/wp-content/uploads/2012/08/667372main\_MSL-EDL-rev-2900.jpg,
		April 9th 2015.
	\bibitem{NASA_youtube}
		NASA,
		\emph{7 Minutes of Terror: Curiosity Rover's Risky Mars Landing},
		https://www.youtube.com/watch?v=h2I8AoB1xgU,
		April 9th 2015.
	\bibitem{Parachute}
		NASA,
		\emph{Mars Science Laboratory Parachute Qualification Testing},
		http://mars.jpl.nasa.gov/msl/news/index.cfm?fuseaction=shownews\&newsid=90,
		April 9th 2015.
	\bibitem{HistoricLanding}
		Chris Gebhardt,
		\emph{Curiosity makes HISTORIC landing at Gale Crater on Mars},
		NASASpaceFlight,
		http://www.nasaspaceflight.com/2012/08/msl-curiosity-historic-martian-landing-at-gale-crater/,
		April 9th 2015.
	\bibitem{CNN_7minterror}
		John Zarella,
		\emph{Mars landing will be ‘seven minutes of terror’},
		CNN,
		http://lightyears.blogs.cnn.com/2012/08/03/8058/,
		April 9th 2015.
	\bibitem{CNNCuriosity}
		Jason Hanna
		\emph{'Impressive' Curiosity landing only 1.5 miles off, NASA says},
		CNN,
		http://edition.cnn.com/2012/08/10/us/mars-curiosity/index.html?eref=mrss\_igoogle\_cnn,
		April 9th 2015.
	\bibitem{MARSwater}
		Nineplanets,
		\emph{Mars},
		http://nineplanets.org/mars.html,
		April 8th 2015
	\bibitem{Wiki-entropy}
		Wikipedia,
		\emph{Entropy},
		March 11th 2015.
	\bibitem{First_radioactivity}
		Wikipedia,
		\emph{Radioactive decay},
		http://en.wikipedia.org/wiki/Radioactive\_decay,
		18.03.2015.
	\bibitem{WikiEarth}
		Wikidedia,
		\emph{Earth}
		http://en.wikipedia.org/wiki/Earth,
		April 7th 2015
	\bibitem{Blood}
		Wikipedia,
		\emph{Blood},
		http://en.wikipedia.org/wiki/Blood,
		April 7th 2015.
	\bibitem{SurviveWater}
		Howstuffworks,
		\emph{Live without food and water},
		http://adventure.howstuffworks.com/survival/wilderness/live-without-food-and-water2.htm,
		April 7th 2015.
	\bibitem{VitalWater}
		Howstuffworks,
		\emph{Water vital to life},
		http://science.howstuffworks.com/environmental/earth/geophysics/water-vital-to-life.htm,
		April 7th 2015.
	\bibitem{WaterContent}
		Healthyeating
		\emph{List of fruits and vegetables with high water content},
		http://healthyeating.sfgate.com/list-fruits-vegetable-high-water-content-8958.html,
		April 7th 2015.
	\bibitem{Darwin}
		Kjetil Lysne Voje,
		\emph{Store norske leksikon - Carles Darwin},
		2014,
		https://snl.no/Charles\_Darwin,
		March 11th 2015.
	\bibitem{tectonic}
		Ivar Ramberg \& Inge Bryhni
		\emph{Store norske leksikon - Platetektonikk}
		2013,
		https://snl.no/platetektonikk,
		February 25th 2015.
	\bibitem{reprod}
		Anton Brøgger \& Store norske leksikon
		\emph{Store norske leksikon, Formering - Biologi},
		https://snl.no/formering\%2Fbiologi,
		March 25th 2015.
	\bibitem{Conway}
		Edwin Martin,
		\emph{John Conway's Game of Life},
		http://www.bitstorm.org/gameoflife,
		March 11th 2015.
	\bibitem{GreekAstro}
		Cristian Violatti,
		\emph{Greek Astronomy},
		http://www.ancient.eu/Greek\_Astronomy/,
		March 18th 2015.
	\bibitem{GalileoTelescope}
		Tammy Plotner,
		\emph{Galileo's Telescope},
		http://www.universetoday.com/15763/galileos-telescope/,
		March 18th 2015.
	\bibitem{Aryabhata}
		\emph{Aryabhata},
		http://www.famous-mathematicians.com/aryabhata/,
		March 18th 2015.
	\bibitem{SpaceAge}
		\emph{The Millennium: A Space and Astronomy Timeline},
		http://www.spacetoday.org/History/MillenniumTimeline/20thCenturyLate.html,
		March 18th 2015.
	\bibitem{Egyptians}
		Martyn Shuttleworth,
		\emph{Egyptian Astronomy},
		https://explorable.com/egyptian-astronomy
		March 18th 2015.
	\bibitem{Eukaryotes}
		C R Woese\, O Kandler\, and M L Wheelis,
		\emph{Towards a natural system of organisms: proposal for the domains Archaea, Bacteria, and Eucarya.},
		http://www.ncbi.nlm.nih.gov/pmc/articles/PMC54159/
		March 28th 2015.
	\bibitem{ProcaEuka}
		 BioMineWiki,
		\emph{Prokaryote versus eukaryote},
		http://wiki.biomine.skelleftea.se/wiki/index.php/Prokaryote\_versus\_eukaryote
		March 28th 2015.
	\bibitem{Lovelock}
		 Lovelock, J.E.
		\emph{Gaia as seen through the atmosphere, Atmospheric Environment (Elsevier), p. 579-580},
		1972.
	\bibitem{shapiro}
		Shapiro, Robert,
		\emph{Origins: A Skeptic's Guide to the Creation of Life on Earth, p. 110},
		Bantam Books,
		1987.
	\bibitem{szosa}
		Alonso, Ricardo\, Szostak\, W. Jack,
		\emph{Life on Earth},
		Scientific American,
		2009.
	\bibitem{FPlan01}
		Mike Wall,
		\emph{Search for Life Guides NASA's New Mars Mission Plan},
		http://www.space.com/15271-nasa-mars-exploration-life-search.html,
		March 28th 2015.
	\bibitem{FPlan02}
		ESA,
		\emph{The ExoMars programme 2016-2018},
		http://exploration.esa.int/mars/46048-programme-overview/,
		March 28th 2015.
	\bibitem{FPlan03}
		WayBackMachine,
		\emph{Tidal Heating, or Satellite Tug-of-War},
		http://web.archive.org/web/20060329000051/http://geology.asu.edu/~glg\_intro/planetary/p8.htm,
		March 28th 2015.
	\bibitem{FPlan04}
		Rolf Haugaard Nielsen,
		\emph{Liv under isen},
		Illustrert vitenskap nr. 5 2015,
		Bonnier Publications International AS
		2015.
	\bibitem{RichOrganics}
		Phys.org,
		\emph{NASA team investigates complex chemistry at Titan},
		http://phys.org/news/2013-04-nasa-team-complex-chemistry-titan.html,
		April 22nd 2015.
	\bibitem{TiME}
		Nell Greenfieldboyce,
		\emph{Exploring A Moon By Boat},
		http://www.npr.org/templates/story/story.php?storyId=112835248,
		April 22nd 2015.
	\bibitem{TALISE}
		Zaina Adamu, Elizabeth Landau,
		\emph{Probe would set sail on a Saturn moon},
		http://lightyears.blogs.cnn.com/2012/10/09/probe-would-set-sail-on-a-saturn-moon/?hpt=hp\_mid,
		April 22nd 2015.
	\bibitem{AVIATR}
		Lillian Ortiz,
		\emph{AVIATR: An Airplane Mission for Titan},
		http://www.universetoday.com/92286/aviatr-an-airplane-mission-for-titan/,
		April 22nd 2015.
	\bibitem{FPlan07}
		ESA,
		\emph{TANDEM/TSSM},
		http://sci.esa.int/tandem-tssm/,
		March 28th 2015.
	\bibitem{Enceladus1}
		Richard A. Lovette,
		\emph{Secret life of Saturn’s moon: Enceladus},
		http://archive.cosmosmagazine.com/features/secret-life-saturns-moon-enceladus/,
		April 22nd 2015
	\bibitem{FPlan09}
		New York Times,
		\emph{Suddenly it seems water is everywhere in solar system},
		http://www.nytimes.com/2015/03/13/science/space/suddenly-it-seems-water-is-everywhere-in-solar-system.html?\_r=0,
		March 28th 2015.
	\bibitem{FPlan10}
		ESA,
		\emph{TSSM NASA/ESA JOINT SUMMARY REPORT},
		http://sci.esa.int/tandem-tssm/44033-tssm-nasa-esa-joint-summary-report/,
		April 22nd 2015.
	\bibitem{FPlan11}
		ESA,
		\emph{Cosmic Vision},
		http://sci.esa.int/cosmic-vision/46510-cosmic-vision/?fbodylongid=2152,
		March 28th 2015.
	\bibitem{FPlan12}
		Mars One,
		\emph{Mars One},
		http://www.mars-one.com/,
		March 28th 2015.
	\bibitem{FPlan13}
		NASA,
		\emph{Mars 2020 Mission Goals},
		http://mars.nasa.gov/mars2020/mission/science/goals/,
		March 28th 2015.
	\bibitem{FPlan14}
		NASA,
		\emph{Mars 2020 Mission},
		http://mars.nasa.gov/mars2020/mission/overview/,
		March 28th 2015.
	\bibitem{EarthAnalysis}
		Allan H. Treiman,
		\emph{Groundbreaking Sample Return from Mars: The Next Giant Leap in Understanding the Red Planet},
		http://www.lpi.usra.edu/decadal/captem/AllanTreimanMars.pdf,
		April 22nd 2015.
	\bibitem{RussiaPlan}
		Zaitsev Yury,
		\emph{Russia To Study Martian Moons Once Again},
		http://www.marsdaily.com/reports/Russia\_To\_Study\_Martian\_Moons\_Once\_Again\_999.html,
		April 22nd 2015.
	\bibitem{ChinaPlan}
		Mars Daily,
		\emph{China to collect samples from Mars by 2030: Xinhua},
		http://www.marsdaily.com/reports/China\_to\_collect\_samples\_from\_Mars\_by\_2030\_Xinhua\_999.html,
		April 22nd 2015.
	\bibitem{FPlan16}
		Jonathan Amos,
		\emph{Where now for Mars exploration?},
		http://www.bbc.com/news/science-environment-17029019,
		March 28th 2015.
	\bibitem{FPlan17}
		NASA,
		\emph{Venus: Facts and Figures},
		solarsystem.nasa.gov/planets/profile.cfm?Object=Venus\&Display=Facts,
		April 22nd 2015..
	\bibitem{FPlan18}
		Cool Cosmos,
		\emph{Could life exist on Venus?},
		http://coolcosmos.ipac.caltech.edu/ask/39-Could-life-exist-on-Venus-,
		March 28th 2015.
	\bibitem{LifeVenus}
		Leslie Mullen,
		\emph{Cloud Colonies on Venus},
		http://web.archive.org/web/20070807083309/http://www.astrobio.net/news/article311.html,
		April 22nd 2015.
	\bibitem{FPlan20}
		Seth Shostak,
		\emph{6 Most Likely Places for Alien Life in the Solar System},
		http://www.space.com/15716-alien-life-search-solar-system.html,
		March 28th 2015.
	\bibitem{FPlan21}
		NASA,
		\emph{Ceres: Overview},
		solarsystem.nasa.gov/planets/proifile.cmf?Object=Dwa\_Ceres,
		April 22nd 2015.
	\bibitem{FPlan22}
		Alan Boyle,
		\emph{Is There Life on Ceres? Dwarf Planet Spews Water Vapor},
		http://www.nbcnews.com/science/space/there-life-ceres-dwarf-planet-spews-water-vapor-n14506,
		March 28th 2015.
	\bibitem{FPlan23}
		NASA,
		\emph{Dawn at a Glance},
		http://www.nasa.gov/mission\_pages/dawn/mission/index.html\#.VRB6mfmG-So,
		March 28th 2015.
	\bibitem{FPlan24}
		Rasmus Kragh Jacobsen,
		\emph{Vandrende plater gir liv under isen},
		Illustrert vitenskap nr. 6 2015,
		Bonnier Publications International AS
		2015
	\bibitem{FPlan25}
		Lisa Grossman,
		\emph{Icy moon explorer gets an Alaska road test},
		http://www.newscientist.com/article/mg22329792.400-icy-moon-explorer-gets-an-alaska-road-test.html\#.VRMTAfmG-Sr,
		March 28th 2015.
	\bibitem{FPlan26}
		William Harris, Jacob Silverman,
		\emph{Are we not the only Earth out there?},
		http://science.howstuffworks.com/other-earth1.htm,
		March 28th 2015.
	\bibitem{OForm1}
		William Bains,
		\emph{Astrobiology},
		http://online.liebertpub.com/doi/abs/10.1089/153110704323175124,
		June 2004, 4(2): 137-167. doi:10.1089/153110704323175124.
	\bibitem{OForm2}
		Car Sagan, Tom Head,
		\emph{Conversations with Carl Sagan},
		https://books.google.no/books?id=gJ1rDj2nR3EC\&printsec=frontcover\&hl=no\#v=onepage\&q\&f=false,
		April 22nd 2015.
	\bibitem{OForm3}
		The Daily Galaxy,
		\emph{Stephen Hawking on Non-Carbon-Based Alien Life},
		http://www.dailygalaxy.com/my\_weblog/2011/05/stephen-hawking-on-non-carbon-based-alien-life.html,
		March 28th 2015.
	\bibitem{OForm4}
		The Living Cosmos,
		\emph{Silicon vs. Carbon},
		http://thelivingcosmos.com/TheNatureofLife/SiliconVsCarbon\_12May06.html,
		March 28th 2015.
	\bibitem{OForm5}
		Norman R. Pace,
		\emph{The universal nature of biochemistry},
		http://www.pnas.org/content/98/3/805.full.pdf,
		March 28th 2015.
	\bibitem{OForm6}
		Liquid Nitrogen Tank .com,
		\emph{How cold is liquid nitrogen?},
		http://liquidnitrogentank.com/how\_cold\_is\_liquid\_nitrogen.php,
		March 28th 2015.
	\bibitem{OForm7}
		David Darling,
		\emph{ammonia-based life},
		http://www.daviddarling.info/encyclopedia/A/ammonialife.html,
		March 28th 2015.
	\bibitem{koonin}
		Koonin, E.V.\, Senkevich, T.G.\, Dolja, V.V.,
		\emph{The Ancient Virus World and Evolution of Cells},
		Biol. Direct.,
		2006.
	\bibitem{villareal}
		Luis P. Villareal,
		\emph{Are Viruses Alive?},
		Scientific American,
		December 2004.
	\bibitem{WaterEverest}
		simplyilka,
		\emph{Do you know why you can’t boil an egg on Mount Everest?},
		http://simplyilka.com/2014/05/22/know-cant-boil-egg-mount-everest/,
		April 21st 2015.
	\bibitem{AtmEarth}
		Wikipedia,
		\emph{Atmosphere of Earth},
		http://en.wikipedia.org/wiki/Atmosphere\_of\_Earth,
		April 21st 2015.
	\bibitem{AtmMars}
		Wikipedia,
		\emph{Atmosphere of Mars},
		http://en.wikipedia.org/wiki/Atmosphere\_of\_Mars,
		April 21st 2015.
	\bibitem{biohack}
		G. Licina\, J. Tibbetts,
		\emph{A Review on Night Enhancement Eyedrops Using Chlorin e6},
		Science for the Masses,
		March 2015.
	\bibitem{nanoblood}
		Casal\, Arancha et. al.,
		\emph{Nanorobots as cellular assistans in inflammatory responses},
		nanorobotdesign.com,
		2004.
	\bibitem{Europa}
		NASA,
		\emph{Europa: Facts \& Figures},
		http://solarsytem.nasa.gov/planets/profile.cmf?Object=Jup\_Europa\&Display=Facts,
		April 22nd 2015.
	\bibitem{Titan}
		NASA,
		\emph{Titan: Facts \& Figures},
		http://solarsystem.nasa.gov/planets/profile.cfm?Object=Sat\_Titan\&Display=Facts,
		April 22nd 2015.
	\bibitem{Enceladus}
		NASA,
		\emph{Enceladus: Facts \& Figures},
		http://solarsystem.nasa.gov/planets/profile.cmf?Object=Sat\_Enceladus\&Display=Facts,
		April 22nd 2015.
	\bibitem{dangers}
		Richard Gray,
		\emph{Dangers of a manned mission to Mars},
		http://www.telegraph.co.uk/news/science/space/10200818/Dangers-of-a-manned-mission-to-Mars.html,
		April 10nd 2015.
	\bibitem{facebook}
		Sebastian Anthony,
		\emph{Facebook’s facial recognition software is now as accurate as the human brain, but what now?},
		http://www.extremetech.com/extreme/178777-facebooks-facial-recognition-software-is-now-as-accurate-as-the-human-brain-but-what-now,
		April 24th 2015.
	\bibitem{artilect}
		Hugo de Garis,
		\emph{The Artilect War},
		ETC Publications,
		1999.
	\bibitem{pearson}
		H. Pearson,
		\emph{Genetics: What is a Gene?},
		Nature 441,
		2006.
	\bibitem{hankgreen}
		Hank Green,
		\emph{Crash Course Biology: DNA Structure and Replication},
		CrashCourse YT,
		Apr. 2. 2012.
	\bibitem{hankgreen2}
		Hank Green,
		\emph{Crash Course Biology: Biological Molecule - You Are What You Eat},
		CrashCourse YT,
		Feb 13. 2012.
	\bibitem{lewontin}
		Anthony J. Griffiths et. al.,
		\emph{Mechanics of DNA Replication},
		An Introduction to Genetic Analysis,
		2000.
	\bibitem{buzz}
		Buzz Lightyear,
		\emph{Toy Story},
		Pixar Studios 1995.
	\bibitem{wow}
		National Geographic Channel,
		\emph{The Wow! signal},
		http://channel.nationalgeographic.com/chasing-ufos/articles/what-is-the-wow-signal/,
		April 28th 2015.
\end{thebibliography}