\initial{H}ow extraordinary to see our journey from the ancient Egyptians' views of the celestial realms to Curiosity landing on the surface of the Red Planet. 
Thanks to our curiosity, the essence of human beings, the world of knowledge is in perpetual progress. 
But \emph{"the more we learn the less we know"} and the philosophical questions around life and our universe remain open.
Where and what is the origin of life? 
We agree on the ingredients needed to form life, but we know little on how these were set together. 
Moreover, is our definition of life too limited? 
Water and carbon are essential for life as we know it today on Earth, but could these be replaced by other substances? 
And if so, is research based on water the right procedure owing to the fact that \emph{"nothing would be more tragic [...] than to encounter alien life and fail to recognize it"} \cite{OForm3}. 
Thanks to the most advanced techniques of communication, laboratory analysis and robot instruments, the rovers based on Mars were able to find and prove earlier presence of water.
It is undeniable that this discovery counts positively on our research of extra-terrestrial life and lead us a step further to answer the most fascinating question: \emph{Are we alone?} 
To answer that question we are forced to search further in our Cosmos, in places like Europa and hopefully new discoveries and new understanding of life await us. 
Even more disturbing and captivating, what if we can seek further in our own definition of life. 
If we fail to find life elsewhere, what about taking the responsibility to produce different life in form of Artificial Intelligence? 
Or what if living things on Earth, like us, are cells part of a bigger organism like the Gaia theory suggests?
Human curiosity has brought us this far, but only future can tell if it will take us \emph{"to the infinity and beyond"} \cite{buzz}.