Planet Earth is often called the blue planet due to the dominant blue areas visible when viewing Earth from space. The blue areas are our vast oceans covering more than 70 \% \cite{WikiEarth} of the surface. These oceans contain and support a broad spectrum of life, and are also a great influence on the climate and weather on Earth. As a matter of fact, all species on Earth are dependent on water in order to survive. A human can only survive for 5 days without water \cite{SurviveWater}, and even extremophiles called xerophiles, dry loving bacteria, needs a tiny amount of water in order to function. In other words, water is essential to life as we know it and therefore extremely interesting. 

A single water molecule consists of three atoms, one oxygen atom and two hydrogen atoms. The two hydrogen atoms are bonded covalently to the oxygen atom. Due to two lone pairs on the oxygen, meaning electrons that are not shared between atoms, the overall structure of the molecule is bent. Further more, the oxygen atom is much more electronegative than the hydrogens creating a dipole moment in the molecule. This means that the oxygen will contain a slight, but significant negative charge while the two hydrogens appear as slightly positive. This creates the basis for the formation of an intricate network of hydrogen bonds as we know that positive and negative charges attracts one another.  

So what makes water so unique? First of all, the formation of hydrogen bonds gives water a high evaporation entalphy and therefore a large evaporation temperature. To transform water from its liquid phase to vapor, energy must be applied bringing water to a temperature of 100 \textcelsius. On the other end of the scale, water will freeze at 0 \textcelsius transforming to ice, which brings us to the second uniqueness of water. In most cases, a solid phase will be denser than a liquid phase making it sink to the bottom \cite{SolidWater}. For water this is not the case, as we all have seen polar bears floating on ice flakes in the Arctic. This phenomenon has had a greater importance than just serving as a fleet for polar bears. Without this property, ice would have sunk to the bottom in repeated cycles until there was no more liquid water during the cold periods in the history of Earth. To sum up, due to chemical and physical properties, water remains liquid over a uniquely broad range of temperatures. The mean temperature on Earth is 15 \textcelsius \cite{WikiEarth} making Earth a perfect place for liquid water. So far we have established that we have a lot of water on Earth, and it occurs mostly in its liquid form. The question remaining is, what is so important with liquid water? 

Liquid water has functions as both a solvent and a transport medium. Both organic and inorganic compounds can be dissolved in water, making it a vital part of the human metabolism. The blood stream is an essential transport network delivering oxygen and nutrients in our body. Human blood plasma, the liquid part of the blood, consists of 92 \% water \cite{Blood}. On Earth we have yet to find an organism completely independent of water. A cucumber has a water content of 96 \%, and the human body is 60 \% water. 


7. april http://healthyeating.sfgate.com/list-fruits-vegetable-high-water-content-8958.html WaterContent

7. april http://en.wikipedia.org/wiki/Earth WikiEarth

7. april http://en.wikipedia.org/wiki/Blood Blood

7. april http://adventure.howstuffworks.com/survival/wilderness/live-without-food-and-water2.htm SurviveWater

http://science.howstuffworks.com/environmental/earth/geophysics/water-vital-to-life.htm VitalWater

7. april https://astrobiology.nasa.gov/ask-an-astrobiologist/answered/2002/05/01/122/ SolidWater