
\paragraph{The ghost in the machine}

In Philip K. Dicks emph{Do Androids Dream of Electric Sheep?}, which was made into the slightly-more-famed movie \emph{Blade Runner}, the protagonist Deckard works as a policeman specializing in catching runaway and criminal androids. In Deckard's world, artificial intelligence has advanced to such a level that telling the difference between a machine and a human being takes expert level knowledge and the application of a variant of the Turing test, a test in which a human judge, holding a conversation with another entity, must deem whether or not that entity is human or machine. 
While Deckard's machines aren't the end-all, be-all of artificial intelligence, they mark the crucial point in coming human history where human beings and machines become indistinguishable to anything but the trained eye. If we can reach a stage where having a conversation with a machine becomes indistinguishable from having a conversation with a regular human being, then can we say that the machine isn't alive? Can something mechanical be infused with a soul? Can something consisting of copper wires and transistors, designed in a lab and built in a factory, be just as living as something made of organic materials? Is it possible that we will \emph{build} life before we discover it?

\paragraph{Architects of our own demise}
The subject of science as a force for destruction is a well-debated issue. Engineering has given us the tools to perform miracles, but also the tools to facilitate our own apocalypse. Recently, debates have grown regarding the future dangers of artificial intelligence - at its highest ideal, artificial intelligence will give birth to entities that seem \emph{god-like} compared to a regular human being. Infinitely higher capacity for information storage and search, instant learning, physical capabilities and endurances so superiour to our own that we will be powerless to stop \emph{should we make enemies of these machines}. This is the \emph{Terminator} endworld nightmare